### 2021-04-14 Chapter-5/Chapter-5.tex
Updates from Overleaf

\begin{table}
\footnotesize
\caption{Evaluation results overview: Name of the benchmark, The Size of the Input Data, The number of leaked functions, The Maximum Leakage, The size of the benchmark, and The Performance.}\label{chapter5:table:over_result}
\centering
\begin{tabular}{lrrrrrrrrrrr}\toprule

\textbf{Benchmark}   & \multicolumn{2}{c}{\textbf{Input Data}} &  \multicolumn{2}{c}{\textbf{\# Functions}} & \multicolumn{2}{c}{\textbf{Maximum Leakage (bits)}}   & \multicolumn{2}{c}{\textbf{Program Size}}    & \multicolumn{3}{c}{\textbf{Performance}}    \\ 
\cmidrule(lr){2-3}\cmidrule(lr){4-5}\cmidrule(lr){6-7}\cmidrule(lr){8-9}\cmidrule(lr){10-12}& \# & bits &  1 Byte &  4 KBs & 1 Byte  & 4 KBs & LoC & Size & Fuzzing & Comparison & Chi-squared
\\\midrule
Unsafe Password Checker& 65536& 16.0& 1&0&0&  & 18 & 104 KB & 21 min & 0.4 min & 0 min\\
Safe Password Checker & 65536 & 16.0& 0&0 &0 &0 & 20 & 106 KB & 20 min & 0.4 min & 0 min\\
One-byte Lookup Table & 65536 & 16.0& 1&1&0&  & 18 & 104 KB & 11 min & 0.1 min & 0 min\\
Four-byte Lookup Table & 65536 & 16.0& 1&1&0&  & 18 & 104 KB & 11 min & 0.1 min & 0 min\\
AES T-Table mbedTLS 2.15 & 65536 & 16.0&2&2&0 &&&&& 1.1 MB &  \\
AES NI mbedTLS 2.15 & 65536 & 16.0&0&0&0 &&&&& 1.1 MB &  \\
AES bitsliced OpenSSL 1.1.0  & 65536 & 16.0 & 2& &0&&&    \\
AES bitsliced OpenSSL 1.1.1& 65536 & 16.0 \\
AES wolfSSL 4.5.0& 65536 & 16.0\\
AES Libgcrypt 1.8.7& 65536 & 16.0\\
RC4 mbedTLS 2.15& 65536 & 16.0\\
RC4 OpenSSL 1.1.0& 65536 & 16.0\\
RC4 OpenSSL 1.1.1& 65536 & 16.0\\
RC4 wolfSSL 4.5.0& 65536 & 16.0\\
RSA mbedTLS 2.15& 4096 & 12.0\\
RSA OpenSSL 1.1.0& 4096 & 12.0\\
RSA OpenSSL 1.1.1& 4096 & 12.0\\
RSA wolfSSL 4.5.0& 4096 & 12.0\\
RSA Libgcrypt 1.8.7& 4096 & 12.0 \\
Tiny DNN & 12000 & 13.6 &\\
GDK 3.24.23 & 65535 & 16.0 &\\
\bottomrule
\end{tabular}

>>>>

\begin{table}
\footnotesize
\caption{Evaluation results overview: Name of the benchmark, The Size of the Input Data, The number of leaked functions, The Maximum Leakage, The size of the benchmark, and The Performance.}\label{chapter5:table:over_result}
\centering
\resizebox{\columnwidth}{!}{
\begin{tabular}{lrrrrrrrrrrr}\toprule

\textbf{Benchmark}   & \multicolumn{2}{c}{\textbf{Input Data}} &  \multicolumn{2}{c}{\textbf{\# Functions}} & \multicolumn{2}{c}{\textbf{Max. Leak (bits)}}   & \multicolumn{2}{c}{\textbf{Program Size}}    & \multicolumn{3}{c}{\textbf{Performance}}    \\ 
\cmidrule(lr){2-3}\cmidrule(lr){4-5}\cmidrule(lr){6-7}\cmidrule(lr){8-9}\cmidrule(lr){10-12}& \# & bits &  1 Byte &  4 KBs & 1 Byte  & 4 KBs & LoC & Size & Fuzzing & Comparison & Chi-squared
\\\midrule
Unsafe Password Checker& 65536& 16.0& 1&0&0&  0& 18 & 104 KB & 21 min & 0.4 min & 0 min\\
Safe Password Checker & 65536 & 16.0& 0&0 &0 &0 & 20 & 106 KB & 20 min & 0.4 min & 0 min\\
One-byte Lookup Table & 65536 & 16.0& 1&1&0&  & 18 & 104 KB & 11 min & 0.1 min & 0 min\\
Four-byte Lookup Table & 65536 & 16.0& 1&1&0&  & 18 & 104 KB & 11 min & 0.1 min & 0 min\\
AES T-Table mbedTLS 2.15 & 65536 & 16.0&2&2&0 &&& 1.1 MB &  \\
AES NI mbedTLS 2.15 & 65536 & 16.0&0&0&0 &&& 1.1 MB &  \\
AES OpenSSL 1.1.0  & 65536 & 16.0 & 2&0 &0&&& 1.0 MB   \\
AES  OpenSSL 1.1.1& 65536 & 16.0 & 2&0 &0&&& 909 KB\\
AES  wolfSSL 4.5.0& 65536 & 16.0 &2&0&0&  &&1.1 MB \\
AES Libgcrypt 1.8.7& 65536 & 16.0 &0 &0 &0& &&4.4 MB\\
RC4 mbedTLS 2.15& 65536 & 16.0 &2 &2 & & & & 1.1 MB\\
RC4 OpenSSL 1.1.0& 65536 & 16.0&2 &2 & & & & 1.0 MB\\
RC4 OpenSSL 1.1.1& 65536 & 16.0&2 &2 & & & & 896 KB\\
RC4 wolfSSL 4.5.0& 65536 & 16.0&2 &2 & & & &886 KB\\
RSA mbedTLS 2.15& 4096 & 12.0 &&&& &&1.8 MB\\
RSA OpenSSL 1.1.0& 4096 & 12.0 &&&& && 11 MB\\
RSA OpenSSL 1.1.1& 4096 & 12.0 &&&& &&13 MB\\
RSA wolfSSL 4.5.0& 4096 & 12.0 &&&& &&4.2 MB\\
RSA Libgcrypt 1.8.7& 4096 & 12.0 &&&& &&4.4 MB\\
Tiny DNN & 12000 & 13.6 & &&&&& 4.4 MB \\
GDK 3.24.23 & 65535 & 16.0 & &&&&& 48 MB\\
\bottomrule
\end{tabular}
}
